### 2016-08-04 README.Rmd
Published
Updated Zenodo badge to final release

[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.16949.svg)](http://dx.doi.org/10.5281/zenodo.16949)

This paper is now in press, and can be cited as:

[White TE, Dalrymple RL, Noble DWA, O’Hanlon JC, Zurek DB, Umbers KDL (2015) Reproducible research in the study of biological colouration. *Animal Behaviour*, in press](http://dx.doi.org/10.1016/j.anbehav.2015.05.007)

>>>>

[![DOI](https://zenodo.org/badge/7271/daniel1noble/colsci_rep.svg)](https://zenodo.org/badge/latestdoi/7271/daniel1noble/colsci_rep)

This paper is now published, and can be cited as:

[White TE, Dalrymple RL, Noble DWA, O’Hanlon JC, Zurek DB, Umbers KDL (2015) Reproducible research in the study of biological colouration. *Animal Behaviour*, 106, 51-57](http://dx.doi.org/10.1016/j.anbehav.2015.05.007)
